---
title: "data_s9_example"
author: "Te-Hsuan Huang"
date: "2025-11-10"
output: github_document
---

```{r}
library(tidyverse)
library(rvest)

set.seed(1)
```
# Z score
```{r}
x_vec = rnorm(30, mean = 5, sd = 3)

(x_vec - mean(x_vec)) / sd(x_vec)
```

# writing a function
* if you did not put Z by itself, the number will not show up
```{r}
z_scores = function(x) {
  
  z = (x - mean(x)) / sd(x)
  z
  
}

z_scores(x_vec)
```

# Try other way
* since we cannot calculate one number for SD

* we cannot calculate for a words and dataset

z_scores(3)

mean(3)
sd(3)

z_scores("my name is jeff")

z_scores(iris)

z_scores(c(TRUE, TRUE, FALSE, TRUE))

# Adding warning
```{r}
z_scores = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) ==1) {
    stop("Z scores cannot be computed for length 1 vectors")
  }
  
  z = mean(x) / sd(x)
  
  z
}
```


# Checking one more time
z_scores(3)

mean(3)
sd(3)

z_scores("my name is jeff")

z_scores(iris)

z_scores(c(TRUE, TRUE, FALSE, TRUE))
