---
title: "Iteration and List Columns"
author: "Te-Hsuan Huang"
date: "2025-11-10"
output: github_document
---

# Loading 
```{r}
library(tidyverse)
library(rvest)

set.seed(1)
```

# List
u can put anything in the list
```{r}
bunch=list(
vec_numeric = 5:8,
vec_char = c("My", "name", "is", "Jeff"),
vec_logical = c(TRUE, TRUE, TRUE, FALSE),
mat=matrix(1:8, nrow=4, ncol=2),
summary=summary(rnorm(100))
)

bunch
```

# output the dataset
```{r}
bunch$vec_numeric

bunch[[1]]

bunch[["vec_numeric"]]
bunch[["vec_numeric"]][1:2]

mean(bunch[["vec_numeric"]])
```

# for loops

step1: create a new list
```{r}
list_norms = 
  list(
    a = rnorm(20, 3, 1),
    b = rnorm(20, 0, 5),
    c = rnorm(20, 10, .2),
    d = rnorm(20, -3, 1)
  )

```

step2: build the function
```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Cannot be computed for length 1 vectors")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)

  tibble(
    mean = mean_x, 
    sd = sd_x
  )
}
```

step3: I can apply that function to each list element.
```{r}
mean_and_sd(list_norms[[1]])
mean_and_sd(list_norms[[2]])
```

step3: let's use alternative way, for loop
```{r}
output = vector("list", length = 4)

for (i in 1:4) {
  output[[i]] = mean_and_sd(list_norms[[i]])
}
```

step3: let's use alternative way, map
```{r}
output2 = map(list_norms, mean_and_sd)
```

### What if u want to do different function
```{r}
output3 = map(list_norms, median)
```

### Make a dataframe

Purpose of .id: It is typically used with functions that return a data frame (map_dfr()) to create a new column in the resulting data frame. This column records the name or index of the element from the original input list (list_norms) that produced that row of data.
```{r}
output4 = map_dbl(list_norms, median, .id = "input")
output5 = map_dfr(list_norms, mean_and_sd, .id = "input")
output6 = map_df(list_norms, mean_and_sd)
output7 = map_df(list_norms, mean_and_sd, .id = "ID")
```

# List columns and operations
```{r}
listcol_df = 
  tibble(
    name = c("a", "b", "c", "d"),
    samp = list_norms
  )
```

```{r}
listcol_df |> pull(name)
listcol_df |> pull(samp)
```

# Operations
```{r}
pull(listcol_df, samp)[[1]]
mean_and_sd(pull(listcol_df, samp)[[1]])
median(pull(listcol_df, samp)[[1]])
```
Use alternative way to calculate the whole list, map
```{r}
map(pull(listcol_df, samp), mean_and_sd)
```

I would like to add output into my dataset
```{r}
listcol_df = 
  listcol_df |> 
  mutate(summary = map(samp, mean_and_sd))

listcol_df

listcol_df |> 
  pull(summary)
```

unnest the dataset
```{r}
listcol_df |> 
  select(-samp) |> 
  unnest(summary)
```

# revisit the data nsduh
```{r}
nsduh_table <- function(html, table_num) {
  
  table = 
    html |> 
    html_table() |> 
    nth(table_num) |>
    slice(-1) |> 
    select(-contains("P Value")) |>
    pivot_longer(
      -State,
      names_to = "age_year", 
      values_to = "percent") |>
    separate(age_year, into = c("age", "year"), sep = "\\(") |>
    mutate(
      year = str_replace(year, "\\)", ""),
      percent = str_replace(percent, "[a-c]$", ""),
      percent = as.numeric(percent)) |>
    filter(!(State %in% c("Total U.S.", "Northeast", "Midwest", "South", "West")))
  
  table
}
```

Try for the for loop
```{r}
nsduh_url = "http://samhda.s3-us-gov-west-1.amazonaws.com/s3fs-public/field-uploads/2k15StateFiles/NSDUHsaeShortTermCHG2015.htm"

nsduh_html = read_html(nsduh_url)

output = vector("list", 3)

for (i in c(1, 4, 5)) {
  output[[i]] = nsduh_table(html=nsduh_html, i)
}

nsduh_results = bind_rows(output)
```

Try for the map
```{r}
nsduh_results = 
  map(c(1, 4, 5), nsduh_table, html = nsduh_html) |> 
  bind_rows()
```

do this all in a dataframe
```{r}
nsduh_results= 
  tibble(
    name = c("marj", "cocaine", "heroine"),
    number = c(1, 4, 5)) |> 
  mutate(table = map(number, nsduh_table, html = nsduh_html)) |> 
  unnest(cols = "table")

nsduh_results
```

# Look at the weather data
```{r}
library(p8105.datasets)
data("weather_df")
```

Nest the data
```{r}
weather_nest = 
  nest(weather_df, data = date:tmin)

weather_nest
```

Using the map
```{r}
weather_lm = function(df) {
  lm(tmax ~ tmin, data = df)
}

weather_lm(pull(weather_nest, data)[[1]])

map(pull(weather_nest, data), weather_lm)
```
# Save in the same dataframe
```{r}
weather_nest = 
  weather_nest |> 
  mutate(models = map(data, weather_lm))

weather_nest
```

