---
title: "Iteration and List Columns"
author: "Te-Hsuan Huang"
date: "2025-11-10"
output: github_document
---

# Loading 
```{r}
library(tidyverse)
library(rvest)

set.seed(1)
```

# List
u can put anything in the list
```{r}
bunch=list(
vec_numeric = 5:8,
vec_char = c("My", "name", "is", "Jeff"),
vec_logical = c(TRUE, TRUE, TRUE, FALSE),
mat=matrix(1:8, nrow=4, ncol=2),
summary=summary(rnorm(100))
)

bunch
```

# output the dataset
```{r}
bunch$vec_numeric

bunch[[1]]

bunch[["vec_numeric"]]
bunch[["vec_numeric"]][1:2]

mean(bunch[["vec_numeric"]])
```

# for loops

step1: create a new list
```{r}
list_norms = 
  list(
    a = rnorm(20, 3, 1),
    b = rnorm(20, 0, 5),
    c = rnorm(20, 10, .2),
    d = rnorm(20, -3, 1)
  )

```

step2: build the function
```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Cannot be computed for length 1 vectors")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)

  tibble(
    mean = mean_x, 
    sd = sd_x
  )
}
```

step3: I can apply that function to each list element.
```{r}
mean_and_sd(list_norms[[1]])
mean_and_sd(list_norms[[2]])
```

step3: let's use alternative way, for loop
```{r}
output = vector("list", length = 4)

for (i in 1:4) {
  output[[i]] = mean_and_sd(list_norms[[i]])
}
```

step3: let's use alternative way, map
```{r}
output2 = map(list_norms, mean_and_sd)
```

### What if u want to do different function
```{r}
output3 = map(list_norms, median)
```

### Make a dataframe

Purpose of .id: It is typically used with functions that return a data frame (map_dfr()) to create a new column in the resulting data frame. This column records the name or index of the element from the original input list (list_norms) that produced that row of data.
```{r}
output4 = map_dbl(list_norms, median, .id = "input")
output5 = map_dfr(list_norms, mean_and_sd, .id = "input")
output6 = map_df(list_norms, mean_and_sd)
output7 = map_df(list_norms, mean_and_sd, .id = "ID")
```

